Certified Knowledge Compilation \\ with Application to Verified Model Counting

### 2023-03-18 doc/mc-paper.tex
minor changes

Finally, the literal denoting the root of the POG is declared with the
{\tt r} command.  It can occur anywhere in the file.  Except in degenerate cases, it
will be the extension variable representing the root of a graph
%, but in
%degenerate cases it can be the positive or negative literal of an
%input variable.

@@

As notation,
let $\psi$ be a subset of the clauses in $\inputformula$.
For partial assignment
$\passign$, the expression  $\simplify{\psi}{\passign}$ denotes the set of clauses $\gamma$
obtained from $\psi$ by: 1) eliminating any
clause containing a literal $\lit$ such that $\passign(\lit) = 1$,
2) for the remaining clauses eliminating those literals $\lit$ for
which $\passign(\lit) = 0$, and 3) eliminating any duplicate clauses.
In doing these simplifications, we also track the {\em provenance}
of each simplified clause $C$, i.e., which of the (possibly multiple) input clauses simplified to become $C$.
More formally, for $C \in \simplify{\psi}{\passign}$, we let $\prov(C, \psi)$ denote
those clauses $C' \in \psi$, such that
$C' \subseteq C \cup \bigcup_{\lit \in \passign} \obar{\lit}$.
We then extend the definition of $\prov$ to any simplified formula
$\gamma$ as $\prov(\gamma, \psi) = \bigcup_{C \in \gamma} \prov(C, \psi)$.

>>>>

Finally, the literal denoting the root of the POG is declared with the
{\tt r} command.  It can occur anywhere in the file.  Except in degenerate cases, it
will be the extension variable representing the root of a graph.
%, but in
%degenerate cases it can be the positive or negative literal of an
%input variable.

@@

As notation,
let $\psi$ be a subset of the clauses in $\inputformula$.
For partial assignment
$\passign$, the expression  $\simplify{\psi}{\passign}$ denotes the set of clauses $\gamma$
obtained from $\psi$ by: i) eliminating any
clause containing a literal $\lit$ such that $\passign(\lit) = 1$,
ii) for the remaining clauses eliminating those literals $\lit$ for
which $\passign(\lit) = 0$, and iii) eliminating any duplicate clauses.
In doing these simplifications, we also track the {\em provenance}
of each simplified clause $C$, i.e., which of the (possibly multiple) input clauses simplified to become $C$.
More formally, for $C \in \simplify{\psi}{\passign}$, we let $\prov(C, \psi)$ denote
those clauses $C' \in \psi$, such that
$C' \subseteq C \cup \bigcup_{\lit \in \passign} \obar{\lit}$.
We then extend the definition of $\prov$ to any simplified formula
$\gamma$ as $\prov(\gamma, \psi) = \bigcup_{C \in \gamma} \prov(C, \psi)$.
